% Setting up document class and essential packages
\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{times}

\begin{document}

% Creating title page
\title{Football Management System: End-Term Project Report}
\author{Your Name}
\date{May 2025}
\maketitle

% Providing abstract
\begin{abstract}
The Football Management System is a web-based application developed using Flask to manage football teams, players, and matches efficiently. This report details the project's objectives, features, technical implementation, and challenges encountered.
\end{abstract}

% Outlining introduction
\section{Introduction}
The Football Management System is a full-stack web application designed to facilitate the management of football teams, their players, and match schedules. Built with Flask, SQLAlchemy, and Bootstrap, it provides a secure and user-friendly interface for CRUD operations and user authentication.

% Listing objectives
\section{Objectives}
\begin{itemize}
    \item Develop a secure and user-friendly web application for football management.
    \item Implement CRUD operations for teams, players, and matches.
    \item Ensure secure user authentication with password hashing.
    \item Support file uploads for player photos with validation.
    \item Utilize Flask Blueprints for modular code organization.
\end{itemize}

% Detailing features
\section{Features}
\begin{itemize}
    \item User registration and login with secure password hashing.
    \item Team management with create, read, update, and delete (CRUD) operations.
    \item Player management with photo uploads.
    \item Match scheduling and search functionality.
    \item Responsive user interface using Bootstrap 5.
\end{itemize}

% Describing database design
\section{Database Design}
The application uses SQLite with SQLAlchemy ORM. The database schema includes:
\begin{itemize}
    \item \textbf{User}: Stores user credentials (username, email, password hash).
    \item \textbf{Team}: Stores team details, linked to a user.
    \item \textbf{Player}: Stores player details, linked to a team.
    \item \textbf{Match}: Stores match details, linked to two teams.
\end{itemize}

% Explaining code structure
\section{Code Structure}
The application is organized using Flask Blueprints for modularity:
\begin{itemize}
    \item \texttt{auth}: Manages user authentication (login, registration, logout).
    \item \texttt{team}: Handles team CRUD operations.
    \item \texttt{player}: Manages player CRUD operations and file uploads.
    \item \texttt{match}: Manages match scheduling and search functionality.
\end{itemize}
Object-oriented principles are applied in models and forms.

% Discussing challenges and solutions
\section{Challenges and Solutions}
\begin{itemize}
    \item \textbf{Challenge}: Ensuring secure file uploads for player photos.
    \item \textbf{Solution}: Implemented validation for file types (JPG, PNG) and size limits.
    \item \textbf{Challenge}: Managing user sessions securely.
    \item \textbf{Solution}: Used Flask sessions with secure cookies and expiration.
    \item \textbf{Challenge}: Preventing unauthorized access to resources.
    \item \textbf{Solution}: Implemented user-based access control in all blueprints.
\end{itemize}

% Summarizing conclusion
\section{Conclusion}
The Football Management System successfully meets all project requirements, demonstrating proficiency in Flask, SQLAlchemy, and modern web development practices. Future enhancements could include advanced analytics and multi-user collaboration features.

\end{document}
